Normalization: A pipeline to analyse time-course gene expression data

### 2019-02-22 scripts/01_quality_control_normalization.Rmd
FIX 01_quality_control_normalization.Rmd
FIX plot in quality_control_normalization

```{r order_genes}
# Reorder genes on condition, time, and replicate

@@

meta["Time"] = as.factor(unlist(meta["Time"]))
meta["Replicate"] = as.factor(unlist(meta["Replicate"]))
par(mfrow=c(1, 2))
autoplot(pca_data, data=meta, colour="Group", shape="Replicate")
autoplot(pca_data, data=meta, colour="Time", shape="Replicate")
```

>>>>

```{r order_genes, fig.width=8, fig.height=4}
# Reorder genes on condition, time, and replicate

@@

# FIXME Add legend
par(mfrow=c(1, 2))
plot(pca_data$x[, "PC1"], pca_data$x[, "PC2"],
     col=ann_colors$Group[meta$Group], pch=16, xlab="PC1", ylab="PC2")
plot(pca_data$x[, "PC1"], pca_data$x[, "PC2"],
     col=ann_colors$Time[meta$Time], pch=16, xlab="PC1", ylab="PC2")

```
